Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa

### 2023-03-09 src/docs_paper/paper.Rmd
S1 Data description and remove mention of Appendix (now S1 Text)

Using risk group proportion estimates, and subnational estimates developed using the Naomi model, we calculated HIV prevalence, PLHIV, HIV incidence and number of new HIV infections stratified by district, age group and risk group.
Further details are provided in Appendix A.2.

@@

Fig \ref{fig:continental-map} and Fig \ref{fig:within-between-country-variation} show posterior mean estimates for the proportion in each risk group from our final model.
Posterior mean, median, and 95\% credible intervals are provided in S1 Data.
In subsequent results, all estimates refer to 2018, the most recent year included in our analysis, unless otherwise indicated.

>>>>

Using risk group proportion estimates, and subnational estimates developed using the Naomi model, we calculated HIV prevalence, PLHIV, HIV incidence and number of new HIV infections stratified by district, age group and risk group.
Further details are provided in S1 Text.

@@

Fig \ref{fig:continental-map} and Fig \ref{fig:within-between-country-variation} show posterior mean estimates for the proportion in each risk group from our final model (provided in S1 Data).
In subsequent results, all estimates refer to 2018, the most recent year included in our analysis, unless otherwise indicated.
